# Data

## Read Data and Description

### Load required library

```{r}
library(readr)
library(tidyverse)
library(dplyr)
library(readr)
```

### Load Data

The dataset was downloaded from xxxxxxxxxxxxxxxxxxxx and saved as "Branded Nutrients 10000.csv".
```{r}
data <- read_csv("Branded Nutrients10000.csv")
```
Guided by the warning, we call problems to understand the issue.
```{r}
problems(data)
```
From the 'problems' above, we know that the issues are due to wrong expected values of some columns where the actual value are decimals (or integers) but the expected is character. Therefore, we read the file again but set these columns to be read as decimals (doubles) to avoid the issue.
```{r}
set_double_col <- unique(problems(data)$col)

# Create a col_types object
col_types_list <- rep("?", ncol(data))  # Default to "guess" for all columns
col_types_list[set_double_col] <- "d"  # Set problematic columns to double ("d")

# Convert to a single string for col_types
col_types_string <- paste(col_types_list, collapse = "")

# Read the CSV with dynamic col_types
data <- read_csv(
  "Branded Nutrients10000.csv",
  col_types = col_types_string
)
```

Display the first few rows
```{r}
head(data)
```


Check column names
```{r}
colnames(data)
```
## Missing value analysis
Check for missing values
```{r}
colSums(is.na(data))
```


