# Data

## Read Data and Description
For this project, we utilized the FoodData Central API provided by the United States Department of Agriculture (USDA) to access detailed nutritional data. This API is designed to help developers incorporate nutrient information into their applications by providing comprehensive documentation about the database structure and data elements. Using this API, we collected data on 10,000 branded food items, capturing 24 features such as brand name, food category, package weight, ingredients, and various nutrients and vitamins. The data were exported to a CSV file and imported into RStudio for analysis. While the dataset is rich in information, we encountered missing values in some fields, particularly for ingredients, as not all foods have complete nutritional details. Despite this, the data offer valuable insights into nutrient composition, enabling us to identify and address gaps in dietary information. The data source is well-documented and regularly updated by the USDA, ensuring reliability and accessibility for research purposes.
### Load required library

```{r}
library(readr)
library(tidyverse)
library(dplyr)
library(readr)
```

### Load Data

The dataset was downloaded from xxxxxxxxxxxxxxxxxxxx and saved as "Branded Nutrients 10000.csv".
```{r}
data <- read_csv("Branded Nutrients_Dataset.csv")
```

Display the first few rows
```{r}
head(data)
```


Check column names
```{r}
colnames(data)
```
## Missing value analysis
Check for missing values
```{r}
colSums(is.na(data))
```


